% MICROSOFT FASTTRACK SENIOR PROGRAM MANAGER — TWO-PAGE VERSION (ATS-SAFE, FACTUAL, POLISHED)

\documentclass[a4paper,11pt]{article}

\usepackage[a4paper,margin=1.65cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{iftex}

% ---------- Fonts ----------
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage[scaled]{helvet}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage{fontspec}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \IfFontExistsTF{Helvetica}{\setmainfont{Helvetica}}{%
    \IfFontExistsTF{Arial}{\setmainfont{Arial}}{\setmainfont{Latin Modern Sans}}}
\fi

\setlist[itemize]{leftmargin=0.17in, itemsep=3pt, topsep=2pt}
\linespread{1.1}
\raggedright

% ---------- Section Formatting ----------
\newcommand{\Section}[1]{%
  \vspace{10pt}%
  {\large\bfseries #1}%
  \vspace{2pt}\par\noindent\hrule height 0.3pt%
  \vspace{4pt}%
}

% ============================================================
\begin{document}

% ============================================================
% PAGE 1
% ============================================================

% ---------- HEADER ----------
{\LARGE\bfseries Juan Cano-Selles}\\[-2pt]
{\small Senior Program Manager — Cloud Platforms, Enterprise Services, ERP-Adjacent Systems}\\[3pt]
\href{mailto:juan.cano.selles@gmail.com}{juan.cano.selles@gmail.com}
\,|\, +49 163 150 9581
\,|\, \href{https://linkedin.com/in/jcanoselles}{linkedin.com/in/jcanoselles}
\,|\, Braunschweig, DE (open to Zürich)

% ---------- PROFILE ----------
\Section{Profile}
\begin{itemize}
  \item Senior Program Manager with 10+ years delivering cloud-based enterprise services, large-scale integrations, and multi-team transformation programs across Europe.
  \item Experienced in aligning engineering, architecture, and business stakeholders to deliver scalable services, streamline operational processes, and drive adoption of new capabilities.
  \item Strong background in Azure-oriented integration patterns, service lifecycle workflows, compliance requirements, and cross-region rollout governance involving 12+ engineering teams.
  \item Automotive domain specialist with a track record of influencing partner teams, reducing delivery risk, and coordinating multi-vendor execution at enterprise scale.
\end{itemize}

% ---------- CORE QUALIFICATIONS ----------
\Section{Core Technical \& Program Qualifications}
\begin{itemize}
  \item Cloud \& Integration: Azure services, API boundaries, monitoring, automation, identity flows; guiding engineering teams through integration and readiness milestones.
  \item Enterprise Processes: Subscription, entitlement, compliance, and regional rollout processes supporting enterprise-scale operational domains.
  \item Customer \& Partner Engagement: CxO and cross-functional stakeholder alignment, delivery assurance, risk identification, mitigation planning, and adoption frameworks.
  \item Program Leadership: OKRs, structured governance cadences, runbooks, risk frameworks, readiness checklists, vendor management, multi-team orchestration.
  \item Data \& Insights: Power BI dashboards for service health, compliance, adoption, and KPI-driven decision-making.
\end{itemize}

% ---------- EXPERIENCE ----------
\Section{Professional Experience}

\vspace{8pt} % ---------- GAP BETWEEN JOBS ----------

% --------- Senior Program Manager - CARIAD ---------
\textbf{Senior Program Manager — Enterprise Cloud Services \& Integration}\\
\textit{CARIAD SE (Volkswagen Group), Wolfsburg, Germany} \hfill {\small Mar 2024 -- Sep 2025}\\[-6pt]
\begin{itemize}
  \item Directed a cross-functional program unifying enterprise service platforms used across global automotive brands, coordinating 12+ engineering, architecture, data, and security teams.
  \item Provided architectural guidance on Azure-based integration, monitoring, automation, and service lifecycle workflows, reducing operational risk across six organizational units.
  \item Introduced program governance (OKRs, risk reviews, rollout readiness), improving delivery predictability and ensuring consistent adoption of new cloud capabilities.
  \item Led engagement with customer-facing and partner teams across Volkswagen Group, improving transparency and alignment on business process impacts.
  \item Managed an 8-figure vendor ecosystem, ensuring consistent delivery quality and alignment to enterprise integration roadmaps.
\end{itemize}

\vspace{8pt} % ---------- GAP BETWEEN JOBS ----------

% --------- Program Manager - Cloud Activation ---------
\textbf{Program Manager — Global Service Activation Platform (ERP-Adjacent)}\\
\textit{CARIAD SE, Wolfsburg, Germany} \hfill {\small Nov 2020 -- Mar 2024}\\[-6pt]
\begin{itemize}
  \item Delivered the global License \& Service Activation Platform for digital services, supporting entitlement, lifecycle, compliance, and onboarding processes aligned to enterprise operational needs.
  \item Scaled the platform from 10k to 4M+ vehicles, coordinating backend, identity, data, QA, compliance, and operations teams across regions.
  \item Achieved 70\% OPEX reduction through automation, architectural simplification, and standardization of cross-team workflows.
  \item Built Power BI dashboards for adoption, service health, KPIs, and compliance reporting, enabling CxO-level visibility and data-driven governance.
  \item Established cross-brand rollout processes to reduce integration risk and improve market deployment readiness.
\end{itemize}

\vspace{8pt} % ---------- GAP BETWEEN JOBS ----------

% --------- SEAT ---------
\textbf{Engineering Program Lead — Connectivity \& Regulatory Services}\\
\textit{SEAT S.A., Barcelona, Spain} \hfill {\small Mar 2019 -- Nov 2020}\\[-6pt]
\begin{itemize}
  \item Delivered the Online Connectivity Unit (OCU) across 20+ EU markets, coordinating engineering, regulatory, QA, and compliance teams; equivalent to multi-region enterprise rollout governance.
  \item Ensured readiness for EU eCall regulatory processes, translating functional and operational requirements across suppliers and internal teams.
  \item Led validation programs (crash, EMC, vibration) ensuring reliability, traceability, and compliance across markets.
\end{itemize}

\vspace{8pt} % ---------- GAP BETWEEN JOBS ----------

% --------- AKKA ---------
\textbf{Systems Integration Engineer — IoT \& Automation}\\
\textit{AKKA Technologies, Barcelona, Spain} \hfill {\small Oct 2015 -- Mar 2019}\\[-6pt]
\begin{itemize}
  \item Built automated CI and testing workflows improving reliability and quality for enterprise-grade connected services.
  \item Coordinated software, QA, and systems engineering workstreams under evolving functional and compliance requirements.
\end{itemize}

% ============================================================
% PAGE 2
% ============================================================

% ---------- EDUCATION ----------
\Section{Education}
\textbf{Master in Engineering — Telecommunication (EQF Level 7)}\\
Miguel Hernández University, Spain — 2013

% ---------- CERTIFICATIONS ----------
\Section{Certifications}
\begin{itemize}
  \item Project Management Professional (PMP), 2025
  \item SAFe Product Owner / Product Manager, 2021
\end{itemize}

% ---------- TECHNICAL SKILLS ----------
\Section{Technical Skills}
\begin{itemize}
  \item \textbf{Cloud \& Integration:} Azure, AWS, API Management, Monitoring, Automation
  \item \textbf{Enterprise Processes:} Entitlement, lifecycle, compliance, rollout governance
  \item \textbf{Data \& Reporting:} Power BI, KPI frameworks, service health dashboards
  \item \textbf{Execution:} OKRs, risk mgmt, dependency mapping, readiness criteria
  \item \textbf{Tools:} Jira, Confluence, CI/CD, distributed systems fundamentals
\end{itemize}

\end{document}