% ============================================================
% CV — JUAN CANO-SELLES
% Master Baseline | English | No Photo | ATS-Safe
% Last reconciled: March 2026
% ============================================================

\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=0.45in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{helvet}

% Layout & Spacing
\renewcommand{\familydefault}{\sfdefault}
\setlist[itemize]{leftmargin=0.18in, itemsep=2pt, topsep=3pt, parsep=1pt, partopsep=0pt}
\linespread{1.1}
\setlength{\parindent}{0pt}

\newcommand{\Section}[1]{%
  \vspace{11pt}%
  {\large\bfseries\uppercase{#1}}%
  \vspace{2pt}\par\noindent\hrule height 0.6pt%
  \vspace{5pt}%
}

\pagestyle{empty}

\begin{document}

% ============================================================
% HEADER
% ============================================================
{\Huge\bfseries JUAN CANO-SELLES} \\[0.5em]
{\large\textbf{Technical Program Manager | Cloud Governance \& Platform Strategy}} \\[0.7em]
Braunschweig, DE \textbar{} \textbf{Open to Relocation} \\[0.3em]
+49 163 150 9581 \textbar{} \href{mailto:juan.cano.selles@gmail.com}{juan.cano.selles@gmail.com} \textbar{} \href{https://www.linkedin.com/in/jcanoselles}{linkedin.com/in/jcanoselles} \\[0.3em]
\textbf{German: C1 \textbar{} English: C2 \textbar{} Availability: 2 Months}

% ============================================================
% EXECUTIVE PROFILE
% ============================================================
\Section{Executive Profile}
Technical Program Manager with 10 years of experience, including 7 years leading cloud platform governance and large-scale infrastructure transformation in the automotive sector. Specialist in orchestrating cross-functional delivery across distributed teams, translating business strategy into executable technical roadmaps, and steering platform convergence programs for global fleets of 10M+ connected endpoints. Combines deep cloud and IoT technical fluency with structured program governance and senior stakeholder management.

% ============================================================
% PROFESSIONAL EXPERIENCE
% ============================================================
\Section{Professional Experience}

\textbf{Sabbatical \& Professional Development} \hfill \textit{Braunschweig, DE $|$ Sep 2025 -- Present}
\begin{itemize}
\item Conducted a structured sabbatical following a 5-year tenure at CARIAD SE: initial travel phase followed by an intensive certification period covering cloud architecture and AI/ML governance.
\item Obtained PMP (2025), AWS Solutions Architect Associate SAA-C03 (2026), and AWS Machine Learning Associate MLA-C01 (2026) certifications.
\item Evaluated MLOps governance patterns and LLM integration frameworks for large-scale cloud environments to formalize expertise in AI-driven platform strategy.
\end{itemize}

\vspace{6pt}
\textbf{CARIAD SE (Volkswagen Group)} $|$ \textbf{Technical Program Manager (Senior Product Owner)} \hfill \textit{Wolfsburg, DE $|$ Nov 2020 -- Aug 2025}
\begin{itemize}
\item Governed the technical roadmap for an Agile Release Train (ART) of five development teams, ensuring global architectural alignment and regulatory compliance for a 10M+ vehicle connectivity platform across brands and markets.
\item Orchestrated portfolio delivery across cloud platform, backend services, data pipelines, security, and operations teams, coordinating dependencies and unified tooling adoption within an 8-figure vendor landscape.
\item Streamlined digital service delivery (Functions-on-Demand activation) by aligning MQTT-based communication protocols and Protobuf definitions between vehicle and cloud backend teams, enabling over-the-air feature monetization for 4M+ connected vehicles.
\item Led the architectural migration from a monolithic legacy system to a microservice-based, event-driven environment (Kafka), scaling global data ingestion and processing pipelines.
\item Engineered and deployed an ML-based behavioral anomaly detection system to identify faulty vehicle communication patterns, proactively deactivating services to prevent battery drain and reduce cloud costs.
\item Enforced a FinOps program achieving a 30\% year-on-year reduction in AWS expenditure through workload migration, resource audits, and refined data access patterns.
\item Drove a cumulative \textasciitilde{}70\% OPEX reduction on the activation platform through cloud-native redesign, automation, and process optimization over the full platform lifecycle.
\item Established a cloud-based test automation platform (Gauge/Jira X-Ray) integrating supplier acceptance tests into deployment pipelines, delivering an automated 360-degree release quality view.
\item Enforced architectural separation and data residency requirements for EU, China, and Canada, ensuring compliance with GDPR and international data sovereignty regulations.
\item Piloted AI initiatives within the internal transformation team: a RAG-based LLM for departmental onboarding and evaluation of PMO automation tooling to reduce administrative overhead.
\end{itemize}

\vspace{6pt}
\textbf{SEAT S.A.} $|$ \textbf{Technical Project Lead} \hfill \textit{Barcelona, ES $|$ Mar 2019 -- Nov 2020}
\begin{itemize}
\item Managed the technical development and series-production integration of connectivity units (OCU) for the SEAT Tarraco, SEAT Leon, and Cupra Born.
\item Steered the end-to-end technical commissioning process, resolving systemic hardware-to-backend authentication (mTLS) bottlenecks to secure vehicle-to-infrastructure connectivity.
\item Coordinated cross-functional deliveries between Tier-1 suppliers and internal departments, managing hardware/software release cycles, wiring schematics, calibration parameters, and technical documentation.
\item Validated full compliance with international homologation standards, supervising EU eCall certifications and safety-critical crash-test preparations across 20+ EU markets.
\end{itemize}

\vspace{6pt}
\textbf{Akkodis} $|$ \textbf{Systems Integration Engineer} \hfill \textit{Barcelona, ES $|$ Oct 2015 -- Mar 2019}
\begin{itemize}
\item Orchestrated technical project coordination and supplier integration for series-production connectivity units as an on-site resident consultant for SEAT S.A.
\item Architected low-level firmware for NFC-based IoT wearables, optimizing power consumption and resolving real-time execution constraints for battery-powered devices.
\item Developed custom Linux drivers and engineered hardware emulators (Python/Qt) to automate communication protocol validation and accelerate software testing workflows for embedded systems.
\item Led software release validation and hardware-in-the-loop (HiL) testing for series-production connectivity units.
\end{itemize}

% ============================================================
% TECHNICAL SKILLS & CERTIFICATIONS
% ============================================================
\Section{Technical Skills \& Certifications}
\begin{itemize}
\item \textbf{Program \& Portfolio Governance:} PMP (2025), SAFe PO/PM (2021), Lean Portfolio Management, Agile/DevOps Governance, PI Planning, Roadmap Development, OKR/KPI Frameworks, FinOps.
\item \textbf{Cloud \& Platform:} AWS Solutions Architect Associate SAA-C03 (2026), AWS Machine Learning Associate MLA-C01 (2026), Event-Driven Architecture (Kafka), Cloud Migration (Azure to AWS), Microservices, CI/CD, Docker, Kubernetes.
\item \textbf{IoT \& Integration:} MQTT, Protobuf, mTLS, IoT Connectivity Platforms, Embedded Systems, HiL Testing.
\item \textbf{Tooling:} Jira (Advanced Roadmaps), Jira X-Ray, Gauge, Confluence, Power BI.
\item \textbf{Languages:} Spanish (Native), English (C2 -- Native Level), German (C1 -- Professional Proficiency), French (B1).
\end{itemize}

% ============================================================
% EDUCATION
% ============================================================
\Section{Education}
\textbf{Master of Science in Telecommunications Engineering} \hfill Miguel Hern\'{a}ndez University, Spain $|$ 2015

\end{document}